Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Some related work
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@18 db7c848b-7755-4df2-b763-8796797afa52

%----------------------------------------------------------------------
\section{Related Work}
%----------------------------------------------------------------------
\label{SEC_related}

In \cite{EMP:09}, we presented the Equalizer parallel rendering framework. This
paper also summarized the work in parallel rendering up to 2009. In the
following we will present the related work published since then. An extensive
Programming and User Guide provides in-depth documentation on using and
programming Equalizer\cite{Eilemann:13}.

\cite{EEP:11} cross-segment load balancing

@@

\cite{NHM:11} ClusterGL?

@@

A canvas can define a frustum, which will create default, planar sub-frusta for
all of its segments. A segment can also define a frustum, which overrides the
canvas frustum, e.g., for non-planar setups such as CAVEs or curved
screens. These frusta describe a physically-correct display setup for a Virtual
Reality installation. A canvas may have a software or hardware swap barrier,
which will synchronize the rendering of all contributing GPUs. The software
barrier executes a \textsf{glFinish} to ensure the GPU is ready to swap, a
Collage barrier (\sref{SEC_barrier}) to synchronize all segments, the swap
buffers call followed by a \textsf{glFlush} to ensure timely execution of the
swap command. The hardware swap barrier is implemented using the
\textsf{WGL\_NV\_swap\_group} or \textsf{GLX\_NV\_swap\_group} extensions.

>>>>

%----------------------------------------------------------------------
\section{Related Work}\label{SEC_related}
%----------------------------------------------------------------------

In~\cite{EMP:09}, we presented the Equalizer parallel rendering framework. This
paper summarized the work in parallel rendering up to 2009. In the following we
will present the related work published since then. An extensive Programming and
User Guide provides in-depth documentation on using and programming
Equalizer~\cite{Eilemann:13}.

The concept of transparent OpenGL interception popularized by WireGL and
Chromium~\cite{HHNFAKK:02} has received little attention. While some commercial
implementations such as TechViz and MechDyne Conduit continue to exists, only
ClusterGL?~\cite{NHM:11} has been published. ClusterGL employs the same approach
as Chromium, but delivers a significantly faster implementation of transparent
OpenGL interception and distribution for parallel rendering.

On the other hand, software for driving and interacting with tiled display walls
has received significant attention. Sage~\cite{TBD} and Sage2~\cite{TBD}

Equalizer itself has received significant attention to research and validate
parallel rendering performance, by using compression and region of interest
during compositing~\cite{MEP:10}, load-balancing resources for multi-display
installations~\cite{EEP:11}, asynchronous compositing and NUMA
optimizations~\cite{EBAHMP:12} as well as work queueing~\cite{SPEP:16}.

Various applications and frameworks have used Equalizer for new research in
visualization, such as the RTNeuron~\cite{HBBES:13}, an OpenGL renderer for
visualizing simulations of neucortical brain regions, Omegalib~\cite{TBD},
extending Equalizer for the hybrid 2D/3D environments such as the CAVE2,
Siegen~\cite{TBD}

@@

@@

A canvas can define a frustum, which will create default, planar sub-frusta for
all of its segments. A segment can also define a frustum, which overrides the
canvas frustum, e.g., for non-planar setups such as CAVEs or curved
screens. These frusta describe a physically-correct display setup for a Virtual
Reality installation. \label{sec:swap} A canvas may have a software or hardware
swap barrier, which will synchronize the rendering of all contributing GPUs. The
software barrier executes a \textsf{glFinish} to ensure the GPU is ready to
swap, a Collage barrier (\sref{SEC_barrier}) to synchronize all segments, the
swap buffers call followed by a \textsf{glFlush} to ensure timely execution of
the swap command. The hardware swap barrier is implemented using the
\textsf{WGL\_NV\_swap\_group} or \textsf{GLX\_NV\_swap\_group} extensions.
